Norming results

### 2021-01-05 osf/comps/data/exp-materials/README.Rmd
restructure osf/comps folder to reflect changes in OSF repo

---
title: "TextGrids"
output:
  github_document:
    html_preview: false
---

@@

This directory contains Praat's `.TextGrid` files corresponding to the `.wav` files in `Raw data/`.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "TextGrids") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Materials"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the images, trial lists, and the results from the norming study.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Materials") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2021-01-05 osf/comps/data/exp-materials/experiment/README.Rmd
restructure osf/comps folder to reflect changes in OSF repo

---
title: "Materials"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the images, trial lists, and the results from the norming study.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Materials") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Norming results"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the results from the norming study.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Materials/Norming results") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```
